---
title: "GAPIT3documentation"
author: "Brian J. Knaus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: GAPIT3doc.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(GAPIT3documentation)
knitr::opts_chunk$set(fig.align = "center")
```


## GAPIT3documentation

```{r}
data("iris")
plot(iris$Sepal.Length, iris$Petal.Length)
```

GAPIT3 publication [@zhang2010mixed].


Method                 | Method paper         | GAPIT Implementation
-----------------------|----------------------|---------------------
CompressionMLM (CMLM)  | @zhang2010mixed      | @lipka2012gapit
gBLUP                  | @zhang2007use        | @lipka2012gapit
Enriched CMLM          | @li2014enrichment    | @tang2016gapit
SUPER                  | @wang2014super       | @tang2016gapit
MLMM                   | @segura2012efficient | @wang2020gapit
FarmCPU                | @liu2016iterative    | @wang2020gapit
cBLUP and sBLUP        | @wang2018expanding   | @wang2020gapit
BLINK                  | @huang2019blink      | @wang2020gapit


# References

