---
title: "GAPIT3documentation glossary"
author: "Brian J. Knaus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GAPIT3documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: GAPIT3doc.bib
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include=FALSE}
library(GAPIT3documentation)
knitr::opts_chunk$set(fig.align = "center")
```


## GAPIT3documentation glossary

**BLINK** Bayesian-information and Linkage- disequilibrium Iteratively Nested Keyway.

**cBLUP and sBLUP** compressed best linear unbiased predictor.

**CMLM** compressed mixed linear model.

**CV** Covariate variables (fixed effects) such as population structure represented by the Q matrix (subpopulation proportion) or principal components (PCs).

**EMMA** efficient mixed model association.

**EMMAX** expedited efficient mixed model association.

**Enriched CMLM** Enriched, compressed mixed linear model.

**FarmCPU** Fixed and random model Circulating Probability Unification.

**G** Genotype data in HapMap format.

**gBLUP** Genomic Best Linear Unbiased Prediction

**genomic BLUP / gBLUP** genomic Best Linear Unbiased Predictor

**GD** Genotype data in numeric format.

**GLM** General linear model

**GM** Genotype map for numeric format.

**GS** genomic prediction and selection.

**GWAS** Genome-wide association studie.

**HapMap format** 

**Heritability**

**KI** Kinship matrix - a sample by sample matrix where the cells describe the relationship among samples and high values represent similar samples.
Random effects.

**MAS** marker assisted selection.

**MLM** mixed linear model.

**MLMM** Multiple locus mixed linear model. (Forward and backward stepwise regression.)

**Numeric format** 

**P3D** population parameters previously determined.

**Q** Population structure.



**SNP** single-nucleotide polymorphism.

**SUPER** Settlement of mixed linear model Under Progressively Exclusive Relationship.

**sBLUP** Settlement of mixed linear model Under Progressively Exclusive Relationship best linear unbiased predictor. (**SUPER gBLUP**.)

**Y** Phenotypic matrix - a sample by trait matrix.
Sample names occur in the first column, traits begin in the second column.













