---
title: "GAPIT3 GLM model"
author: "Brian J. Knaus"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic_example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
bibliography: GAPIT3doc.bib
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include=FALSE}
#library(GAPIT3documentation)
knitr::opts_chunk$set(fig.align = "center")
```



## GLM

The **G**eneral **L**inear **M**odel [@lipka2012gapit] (not to be confused with the *generalized* linear model)

$$
y = s + Q + \epsilon_{ \mathcal{N}(0,\,\sigma^{2}) } 
$$

- $y$ is a vector of phenotypic measurements
- $s$ genotypes
- $Q$ indicates population structure (a categorical indicator) 
- $\epsilon_{dnorm}$ is normally distributed error


The $Q$ matrix may be obtained from clustering algorithms such as 'admixture', 'DAPC', 'kmeans', 'STRUCTURE', or '[fastSTRUCTURE](https://rajanil.github.io/fastStructure/).'


## Example code


```
  myPhenoFile <- system.file("extdata", "mdp_traits.txt.gz",
                             package = "GAPIT3")
  myGenoFile <- system.file("extdata", "mdp_genotype_test.hmp.txt.gz",
                            package = "GAPIT3")
  
  myPhenotypes <- read.table(myPhenoFile, header = TRUE)
  myPhenotypes <- myPhenotypes[, 1:3]
  myGenotypes  <- read.table(myGenoFile, header = FALSE)
  
  myGAPIT <- GAPIT( Y = myPhenotypes,
                    G = myGenotypes,
                    PCA.total = 3,
#                    file.output = TRUE,
                    file.output = FALSE,
                    maxLoop = 1,
                    model = "GLM"
  )
```


## GAPIT flowchart


* GAPIT() - manages multiple models, calls GAPIT.DP()
  * GAPIT.DP() - doesn't much more than call GAPIT.Genotype(), omit.
    * GAPIT.Genotype()
      * GAPIT.kinship.*()
  * GAPIT.Phenotype.View() - create graphic for one phenotypic trait
  * GAPIT.Judge() - mostly catch inappropriate combinations of input
  * GAPIT.IC() - Intermediate Components
  * GAPIT.SS() - Sufficient Statistics, Z is created, stats::lm
    * GAPIT.Main()
  
  
  
    * GAPIT.Bus() - Returens GWAS from GAPIT()
      * GAPIT() <- is this recursion???


## Returned files






___
___

# References




